The formal verification of the ctm approach to forcing \thanks{Supported by Secyt-UNC projects 33620180100855CB and 33620180100465CB, and Conicet.}

### 2022-10-30 Independence_CH/related.tex
Related & corrected bib. Pruned header

A sweet spot combining the best of both worlds is to be found on
developments in Isabelle/HOL based on the AFP entry
\session{ZFC\_in\_HOL} by Paulson \cite{ZFC_in_HOL-AFP}. There is a
range of results in combinatorics and other set-theoretical material
that was swiftly formalized in this setting: Nash-Williams theorem and
Larson's $\forall k\ \omega^{\omega}\longrightarrow(\omega^\omega,k)$
\cite{doi:10.1080/10586458.2021.1980464}, Design Theory
\cite{10.1007/978-3-030-81097-9_1}, and Wetzel's problem
\cite{2022arXiv220503159P}; this last paper describes in a brief and
clear way the convenience of the interaction with Isabelle/HOL
(which is also paid in consistency-strength currency
\cite[Sect.~3]{DBLP:conf/ictac/Obua06}).

>>>>

A sweet spot combining the best of both worlds is to be found on
developments in Isabelle/HOL based on the AFP entry
\session{ZFC\_in\_HOL} by Paulson \cite{ZFC_in_HOL-AFP}. There is a
range of results in combinatorics and other set-theoretical material
that was swiftly formalized in this setting: Erdős-Milner
partition theorem \cite{2021arXiv210411613P}, Nash-Williams theorem and
Larson's $\forall k\ \omega^{\omega}\longrightarrow(\omega^\omega,k)$
\cite{doi:10.1080/10586458.2021.1980464}, Design Theory
\cite{10.1007/978-3-030-81097-9_1}, and Wetzel's problem
\cite{2022arXiv220503159P}; this last paper describes in a brief and
clear way the convenience of the interaction with Isabelle/HOL
(which is also paid in consistency-strength currency
\cite[Sect.~3]{DBLP:conf/ictac/Obua06}).
